Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
reformat renv link, mention sevenbridges in README
Add draft based on https://hackmd.io/@Sq-NZxXnQQGtVzoZDwyznA/Sk0ijR8IV

- [`renv` with Docker](https://rstudio.github.io/renv/articles/docker.html)

@@

- researchcompendia.science
- https://github.com/benmarwick/rrtools
- \pkg{renv}, https://rstudio.github.io/renv/articles/docker.html
- what to copy in and what not

>>>>

**\pkg{renv}** ([https://rstudio.github.io/renv/](https://rstudio.github.io/renv/)) with Docker: https://rstudio.github.io/renv/articles/docker.html

@@

- researchcompendia.science
- https://github.com/benmarwick/rrtools

Containers provide a high degree of isolation that is often desirable when attempting to capture a specific computational environment so that others can reproduce and extend a research result. Many computationally intensive research projects depend on specific versions of original and third-party software packages in diverse languages, joined together to form a  pipeline through which data flows. New releases of even just a single piece of software in this pipeline can break the entire workflow, making it difficult for others to use, and making the original the results irreproducible. The chance of a substantial disruption like this is high in a multi-year research project where key pieces of third-party software may have several major updates over the duration of the project. Containers give the researcher an isolated environment to assemble these research pipelines with specific versions of software. Research workflows in containers are safe from contamination from other activities occuring on the researcher's computer, for example the installation of newest version of packages for teaching demonstrations.

In many fields we see that a typical unit of research for a container is a research report or journal article, where the container holds the compendium, or self-contained set of data (or connections to data elsewhere) and code files needed to fully reproduce the article [@doi:10.1080/00031305.2017.1375986]. Images of compendium containers can be hosted on services such as Docker Hub for convienient sharing among collaborators and others. Similarly, packages such as containerit and dockerfiler can be used to create a Dockerfile to be archived with a compendium on a data repository (e.g. Zenodo, Dataverse, Figshare, OSF). A typial compendium Dockerfile will pull a rocker image fixed to a specific version of R, and install R packages from the MRAN repository to ensure the package versions are tied to a specific date, rather than the most recent version. A future researchers can download then compendium from the repository and run the included Dockerfile build a new image that recreates the computational environment used to produce the original research results.

- \pkg{renv}, https://rstudio.github.io/renv/articles/docker.html
- what to copy in and what not
